A spiral galaxy's mass distribution uncovered through lensing and dynamics

### 2015-09-11 docs/results_JAMwithSB_v1.01.tex
Finished discussion on stellar mass-to-light ratios.
Removed some TO DOs.

\subsection{JAM based on Surface Brightness}

\paragraph{... with the Lens Mass Model.} Our first JAM model uses the mass distribution which we found from lensing constraints in \S\ref{sec:results_lensing} to generate an independent prediction for the $v_\text{rms}$ curve following the procedure in \S\ref{sec:model_JAM}. In addition to the flat rotation curve model with $\alpha = 1$ in Table \ref{tab:bestfitlensmodel}, we also investigate a lens model, which was found as a best fit to the lensing images when assuming a [TO DO: rising or droppint???] rotation curve slope of $\alpha=1.1$. The predictions are compared with the data in Figure \ref{fig:JAM_modelL}. The agreement between the lensing prediction and the observed kinematics within $R' \sim 3$ arcsec is striking, especially around the Einstein radius. The $\alpha = 1$ model fits the wings nicely, while the $\alpha = 1.1$ model recreates almost exactly the observed central dip. The sharp drop in $v_\text{rms}$ around $R' \sim 3$ arcsec [TO DO: make sure all projected Rs are $R'$] cannot be reproduced, however. But outside of the Einstein radius our lensing models are only extrapolations and the true constraint is around the Einstein radius.

@@

\begin{figure}
  \centering
  \includegraphics[height=6cm]{fig/lensing_JAM_comparision.ps}
  \caption{Comparison (not a fit!) of the symmetrized stellar $v_\text{rms}$ data of J1331 (blue dots) with JAM models generated from mass distributions which were independently derived from lensing constraints in \S\ref{sec:results_lensing}. The red solid line corresponds to the lens model for a flat rotation curve ($\alpha = 1$) in Table \ref{tab:bestfitlensmodel}; the green line is a best fit lens model found analogously from the image positions, but for a fixed rotation curve slope of $\alpha = 1.1$. For the JAM modelling a best fit MGE to the lens mass models were used, as well as the observed surface brightness MGE in Table \ref{tab:MGEF814W}, assuming velocity isotropy $\beta_z = 0$ and an inclination of $i = 70^\circ$.The red and black dotted lines are the Einstein radius and the effective half-light radius, respectively.}
  \label{fig:JAM_modelL}
\end{figure}

@@

\paragraph{... with "Mass-follows-Light" and Velocity Anisotropy.} Our second JAM model is a mass-follows-light model, which are often used in dynamical JAM modelling (e.g. \citet{GlennEC,Cap06}), where the mass distribution ins generated by multiplying the light distribution in Table \ref{tab:MGEF814W} by a constant total mass-to-light ratio  $\Upsilon_{I,\text{tot}}^\text{dyn}$. This assumes that the dark matter is always a constant fraction of the total matter distribution everywhere. This simplified model sometimes gives good representations of the inner parts of galaxies, where the stellar component dominates. Testing this model for J1331 is also motivated by our findings from lensing in Section \ref{sec:results_lensing}, where around the Einstein radius total and luminous mass seem to have a similar distribution.
\\In addition to the free fit parameter  $\Upsilon_{I,\text{tot}}^\text{dyn}$, we also allow for a overall constant but non-zero velocity anisotropy $\beta_z$. The best fit is found by minimizing $\chi^2$ between the $v_\text{rms}$ data and model prediction and is demonstrated in Figure \ref{fig:JAM_modelA2}. For $\beta_z$ we impose the fitting limits $\beta_z \in [-0.5,+0.5]$. While the outer parts of galaxies often show radially biased velocity anisotropy up to $\sim 0.5$ (from dynamical modelling of observed elliptical galaxies (e.g. \citet{Kronawitter2000}) and cosmological simulations (e.g. \citet{2004MNRAS.352..535D,2001ApJ...557..533F}), the centers of galaxies are near-isotropic or have  negative velocity anisotropy \citep{2003ApJ...583...92G}. Only in extreme models (e.g. around in-spiralling supermassive black holes \citep{1997NewA....2..533Q}) velocity anisotropies as low as $\sim -1$ have been found. A lower limit of $\beta_z \geq -0.5$ is a realistic assumption for J1331, for which we do not expect extreme dynamical conditions. The best fit in Figure \ref{fig:JAM_modelA2} however strives to very negative velocity anisotropies to be able to get the deep central dip in the  $v_\text{rms}$ curve. But $\beta_z = -0.5$ is not even a remotely agreeable fit and lower anisotropies are not to be expected and realistic. We also tested radial profiles for $\beta_z(R)$ of the form proposed by \citet{BaesVanHese}, which was however equally unable to reproduce the data. We conclude, that this is due to the well-known degeneracy between anisotropy and mass profile [TO DO: REF] and the mass-follows-light model is \emph{not} a good representation of the mass distribution in J1331's inner regions.

@@

\paragraph{... with Increasing Mass-to-Light Ratio.} In \S\ref{sec:results_lensing} we found from the lensing, that the light distribution might drop faster with radius than the mass distribution. This would correspond to a radially increasing total mass-to-light ratio. As velocity anisotropy alone cannot explain the observed kinematics in a simple a mass-follows-light model, we now allow for an mass-to-light ratio gradient in the JAM modelling to generate a mass model from the light distribution in Table \ref{tab:MGEF814W}. We do this by assigning each of the five Gaussians in the MGE its own mass-to-light ratio and replace the total luminosity in Eq. (\ref{eq:centralItotalL}) $L_i$ with the Gaussians total Mass $M_i = \Upsilon_{i} L_i$. We treat the five $\Upsilon_i$ as free parameters and only require that $\Upsilon_{j} \geq \Upsilon_i$ when the corresponding $\sigma_j \geq \sigma_i$ to ensure an overall mass-to-light ratio that is increasing with radius.
\\Figure \ref{fig:enclMass_modelG} shows the (local projected) mass-to-light ratio gradient generated by the best fit to the dynamics data, which rises from $\Upsilon_\text{tot} = 2.53$ in the center and approaches a value of $\Upsilon_\text{tot}$ outside of the fitted region at $R'\gtrsim 3$ arcsec of $\Upsilon_\text{tot} = 7.60)$. The central mass-to-light ratio corresponds to the Chabrier IMF stellar mass-to-light ratio found by [TO DO: REF: TREU ET AL 2011] $\Upsilon_{i,*}^\text{Chab} = 2.5 \pm 0.6$ [TO DO: introduce and explain????]. The strong rise  of$\Upsilon_\text{tot}(R')$ cannot be explained by an increase in the stellar $\Upsilon_*$ alone [TO DO: Really??? Maybe it would have dropped again in the blue disk, if I had allowed for it????], so we deduce that we might need  contribution of dark matter halo in J1331.
\\Fig. \ref{fig:JAM_modelG} shows that the best fit model greatly reproduces the central dip in the $v_\text{rms}$ curve, even though it has slight problems fitting the drop around $R' \sim 4$ arcsec. The latter might be because we only allowed the $\Upsilon_\text{tot}(R')$ to rise. A slight drop could be expected when the reddish bulge turns into the bluish disk and the contribution of the stellar component becomes less due to a lower $\Upsilon_{*}$ for younger and bluer populations.
\\In Fig. \ref{fig:enclMass_modelG} we overplot the enclosed mass profile with the Einstein mass $M_\text{ein} = (7.77 \pm 0.33) \cdot 10^{10} M_\odot$ at the Einstein radius found from lensing in Table [TO DO: REF]. The agreement between the Einstein mass and the independently found $M(<R_\text{ein}) = 7.49 \cdot 10^{10} M_\odot$ from dynamical modelling is striking.

@@

\begin{figure*}
\centering
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[height=6cm]{fig/jam_G_vrms.ps}
  \caption{Comparison of $v_\text{rms}$ data and best fit model.}
  \label{fig:JAM_modelG}
\end{subfigure}%
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[height=6cm]{fig/jam_G_enclMass.ps}
  \caption{Enclosed mass and mass-to-light ratio profile. [TO DO: Make figure wider. Include legend.???] [TO DO: weird  ticks on right axis???] [TO DO: Why does this plot look different than the others???] [TO DO: Switch the two y-axes. It's better to have ML on the left side, to read up the central ML.]}
  \label{fig:enclMass_modelG}
\end{subfigure}
\caption{JAM model found by fitting an increasing total mass-to-light ratio $\Upsilon_\text{tot}$ profile used to generate a mass model from the light distribution.  This is done by assigning a different mass-to-light ratio to each Gaussian in the MGE in Table \ref{tab:MGEF814W}. \emph{Panel (a):} Comparison between the stellar $v_\text{rms}$ data (blue points) and the best fit model (green line). \emph{Panel (b):} Enclosed mass inside the projected radius $R'$ on the sky (green line, left axis) and mass-to-light profile $\Upsilon(R')$ along the major axis [TO DO: CHECK???] (blue line, right axis) of the best fit model. The enclosed mass curve is overplotted with the independent finding for the Einstein mass $\pm 4 \%$ in Table [TO DO: TABLE REFERENCE???] (red dot) at the Einstein radius (red dotted line). The best fit mass-to-light ratios of the first four Gaussians are plotted against each Gaussians $\sigma$ (yellow stars). The two Gaussians with the largest $\sigma$ (the fifth is not shown) have the same best fit mass-to-light ratio. Overplotted is also the effective half-light ratio $R_\text{eff}$ (black dotted line).}
\label{fig:modelG}
\end{figure*}

>>>>

\subsection{JAM based on Surface Brightness} \label{sec:results_JAM_SB}

\paragraph{... with the Lens Mass Model.} Our first JAM model uses the mass distribution which we found from lensing constraints in Section \ref{sec:results_lensing} to generate an independent prediction for the $v_\text{rms}$ curve following the procedure in Section \ref{sec:model_JAM}. In addition to the flat rotation curve model with $\alpha = 1$ in Table \ref{tab:bestfitlensmodel}, we also investigate a lens model, which was found as a best fit to the lensing images when assuming a [TO DO: rising or droppint???] rotation curve slope of $\alpha=1.1$. The predictions are compared with the data in Figure \ref{fig:JAM_modelL}. The agreement between the lensing prediction and the observed kinematics within $R' \sim 3$ arcsec is striking, especially around the Einstein radius. The $\alpha = 1$ model fits the wings nicely, while the $\alpha = 1.1$ model recreates almost exactly the observed central dip. The sharp drop in $v_\text{rms}$ around $R' \sim 3$ arcsec cannot be reproduced, however. But outside of the Einstein radius our lensing models are only extrapolations and the true constraint is around the Einstein radius.

@@

\begin{figure}
  \centering
  \includegraphics[height=6cm]{fig/lensing_JAM_comparision.ps}
  \caption{Comparison (not a fit!) of the symmetrized stellar $v_\text{rms}$ data of J1331 (blue dots) with JAM models generated from mass distributions which were independently derived from lensing constraints in Section \ref{sec:results_lensing}. The red solid line corresponds to the lens model for a flat rotation curve ($\alpha = 1$) in Table \ref{tab:bestfitlensmodel}; the green line is a best fit lens model found analogously from the image positions, but for a fixed rotation curve slope of $\alpha = 1.1$. For the JAM modelling a best fit MGE to the lens mass models were used, as well as the observed surface brightness MGE in Table \ref{tab:MGEF814W}, assuming velocity isotropy $\beta_z = 0$ and an inclination of $i = 70^\circ$.The red and black dotted lines are the Einstein radius and the effective half-light radius, respectively.}
  \label{fig:JAM_modelL}
\end{figure}

@@

\paragraph{... with "Mass-follows-Light" and Velocity Anisotropy.} Our second JAM model is a mass-follows-light model, which are often used in dynamical JAM modelling (e.g. \citet{GlennEC,Cap06}), where the mass distribution ins generated by multiplying the intrinsic light distribution $\nu(R,z)$ (the MGE given in Table \ref{tab:MGEF814W} deprojected according to the inclination) by a constant total mass-to-light ratio  $\Upsilon_{I,\text{tot}}^\text{dyn}$. This assumes that the dark matter is always a constant fraction of the total matter distribution everywhere. This simplified model sometimes gives good representations of the inner parts of galaxies, where the stellar component dominates. Testing this model for J1331 is also motivated by our findings from lensing in Section \ref{sec:results_lensing}, where around the Einstein radius total and luminous mass seem to have a similar distribution.
\\In addition to the free fit parameter  $\Upsilon_{I,\text{tot}}^\text{dyn}$, we also allow for a overall constant but non-zero velocity anisotropy $\beta_z$. The best fit is found by minimizing $\chi^2$ between the $v_\text{rms}$ data and model prediction and is demonstrated in Figure \ref{fig:JAM_modelA2}. For $\beta_z$ we impose the fitting limits $\beta_z \in [-0.5,+0.5]$. While the outer parts of galaxies often show radially biased velocity anisotropy up to $\sim 0.5$ (from dynamical modelling of observed elliptical galaxies (e.g. \citet{Kronawitter2000}) and cosmological simulations (e.g. \citet{2004MNRAS.352..535D,2001ApJ...557..533F}), the centers of galaxies are near-isotropic or have  negative velocity anisotropy \citep{2003ApJ...583...92G}. Only in extreme models (e.g. around in-spiralling supermassive black holes \citep{1997NewA....2..533Q}) velocity anisotropies as low as $\sim -1$ have been found. A lower limit of $\beta_z \geq -0.5$ is a realistic assumption for J1331, for which we do not expect extreme dynamical conditions. The best fit in Figure \ref{fig:JAM_modelA2} however strives to very negative velocity anisotropies to be able to get the deep central dip in the  $v_\text{rms}$ curve. But $\beta_z = -0.5$ is not even a remotely agreeable fit and lower anisotropies are not to be expected and realistic. We also tested radial profiles for $\beta_z(R)$ of the form proposed by \citet{BaesVanHese}, which was however equally unable to reproduce the data. We conclude, that this is due to the well-known degeneracy between anisotropy and mass profile [TO DO: REF] and the mass-follows-light model is \emph{not} a good representation of the mass distribution in J1331's inner regions.

@@

\paragraph{... with Increasing Mass-to-Light Ratio.} In Section \ref{sec:results_lensing} we found from the lensing, that the light distribution might drop faster with radius than the mass distribution. This would correspond to a radially increasing total mass-to-light ratio. As velocity anisotropy alone cannot explain the observed kinematics in a simple a mass-follows-light model, we now allow for an mass-to-light ratio gradient in the JAM modelling to generate a mass model from the light distribution in Table \ref{tab:MGEF814W}. We do this by assigning each of the five Gaussians in the MGE its own total mass-to-light ratio $\Upsilon_{\text{I,tot},i}$ and replace the total luminosity in Equation \ref{eq:centralItotalL} $L_i$ with the Gaussians total Mass $M_i = \Upsilon_{\text{I,tot},i} L_i$. We treat the five $\Upsilon_{\text{I,tot},i}$ as free parameters and only require that $\Upsilon_{\text{I,tot},j} \geq \Upsilon_{\text{I,tot},i}$ when the corresponding $\sigma_j \geq \sigma_i$ to ensure an overall mass-to-light ratio that is increasing with radius.
\\Figure \ref{fig:enclMass_modelG} shows the (local projected) mass-to-light ratio gradient generated by the best fit to the dynamics data, which rises from $\Upsilon_\text{tot} = 2.53$ in the center and approaches a value of $\Upsilon_\text{tot}$ outside of the fitted region at $R'\gtrsim 3$ arcsec of $\Upsilon_\text{tot} = 7.60)$. The central mass-to-light ratio corresponds to the Chabrier IMF stellar mass-to-light ratio found by [TO DO: REF: TREU ET AL 2011] $\Upsilon_{i,*}^\text{Chab} = 2.5 \pm 0.6$ [TO DO: introduce and explain????]. The strong rise of $\Upsilon_\text{tot}(R')$ cannot be explained by an increase in the stellar $\Upsilon_*$ alone [TO DO: Really??? Maybe it would have dropped again in the blue disk, if I had allowed for it????], so we deduce that we might need  contribution of dark matter halo in J1331.
\\Figure \ref{fig:JAM_modelG} shows that the best fit model greatly reproduces the central dip in the $v_\text{rms}$ curve, even though it has slight problems fitting the drop around $R' \sim 4$ arcsec. The latter might be because we only allowed the $\Upsilon_\text{tot}(R')$ to rise. A slight drop could be expected when the reddish bulge turns into the bluish disk and the contribution of the stellar component becomes less due to a lower $\Upsilon_{*}$ for younger and bluer populations.
\\In Figure \ref{fig:enclMass_modelG} we overplot the enclosed mass profile with the Einstein mass $M_\text{ein} = (7.77 \pm 0.33) \cdot 10^{10} M_\odot$ at the Einstein radius found from lensing in Table [TO DO: REF]. The agreement between the Einstein mass and the independently found $M(<R_\text{ein}) = 7.49 \cdot 10^{10} M_\odot$ from dynamical modelling is striking.

@@

\begin{figure*}
\centering
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[height=6cm]{fig/jam_G_vrms.ps}
  \caption{Comparison of $v_\text{rms}$ data and best fit model.}
  \label{fig:JAM_modelG}
\end{subfigure}%
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[height=6cm]{fig/jam_G_enclMass.ps}
  \caption{Enclosed mass and mass-to-light ratio profile. [TO DO: Make figure wider. Include legend.???] [TO DO: weird  ticks on right axis???] [TO DO: Why does this plot look different than the others???] [TO DO: Switch the two y-axes. It's better to have ML on the left side, to read up the central ML.] [TO DO: local mass to light ratio $\Upsilon_\text{I,tot}(R')$]}
  \label{fig:enclMass_modelG}
\end{subfigure}
\caption{JAM model found by fitting an increasing total mass-to-light ratio $\Upsilon_\text{tot}$ profile used to generate a mass model from the light distribution.  This is done by assigning a different mass-to-light ratio to each Gaussian in the MGE in Table \ref{tab:MGEF814W}. \emph{Panel (a):} Comparison between the stellar $v_\text{rms}$ data (blue points) and the best fit model (green line). \emph{Panel (b):} Enclosed mass inside the projected radius $R'$ on the sky (green line, left axis) and mass-to-light profile $\Upsilon(R')$ along the major axis [TO DO: CHECK???] (blue line, right axis) of the best fit model. The enclosed mass curve is overplotted with the independent finding for the Einstein mass $\pm 4 \%$ in Table [TO DO: TABLE REFERENCE???] (red dot) at the Einstein radius (red dotted line). The best fit mass-to-light ratios of the first four Gaussians are plotted against each Gaussians $\sigma$ (yellow stars). The two Gaussians with the largest $\sigma$ (the fifth is not shown) have the same best fit mass-to-light ratio. Overplotted is also the effective half-light ratio $R_\text{eff}$ (black dotted line).}
\label{fig:modelG}
\end{figure*}

### 2015-09-11 docs/results_photometry_v1.01.tex
Revistied most of the lensing section.
Removed some TO DOs.

\subsection{Surface Photometry for J1331 with MGEs}

@@

\begin{figure}
\centering
\includegraphics[width=0.8\columnwidth]{fig/1331F814Wsci_MGE_M.ps}
\caption{MGE for J1331's inner regions: Comparison of contours with constant F814W surface brightness of J1331's central region (orange lines) with the corresponding iso-brightness contours of the best fit MGE in table \ref{tab:MGEF814W}, convolved with the PSF in table \ref{tab:MGEF814W}, (gray lines). The MGE model is a good representation of the galaxy's light distribution within $\sim 5$ arcsec. Image scaling and orientation are indicated in the figure. The black line has a length of 10 arcsec and it's orientation corresponds to the galaxy's position angle as found in table \ref{tab:galaxyparameters}. For comparison the Einstein radius as found in table ??? is indicated as red dashed line. This MGE is used in the dynamical Jeans modelling in \S ???. [TO DO: explain how this MGE is used in dynamical modelling]}
\label{fig:MGEinnerRegions}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=0.8\columnwidth]{fig/1331F814W_MGE_disk_L.ps}
\caption{MGE for J1331's outer regions: Comparison of contours with constant surface brightness of the smooth IRAF ELLIPSE model for J1331 in the F814W filter (yellow) with a corresponding best fit MGE (gray lines). The green box corresponds to the image section shown in Fig. \ref{fig:MGEinnerRegions}, with the Einstein radius as dashed red line. [TO DO: caption]}
\label{fig:MGEouterRegions}
\end{figure}

@@

\begin{table}
\centering
\caption{F814W PSF MGE: Parameters of the circular four-Gaussian MGE in Eq. (\ref{eq:PSFgeneral} fitted to the radial profile of the synthetic HST/F814W PSF image by [TO DO].}
\begin{tabular}{ccc}
\hline
$k$ & $G_k$ & $\delta_k$ [arcsec] \\\hline
1 & 0.184 & 0.038\\
2 & 0.485 & 0.085\\
3 & 0.222 & 0.169\\
4 & 0.109 & 0.487\\\hline
\end{tabular}
\label{tab:PSFMGEF814W}
\end{table}

\begin{table*}
\centering
\caption{J1331's F814W MGE: Parameters of the best fit MGE to the F814W surface brightness of J1331 in Fig. \ref{fig:F814W}. The fit is best inside an radius of 5 arcsec. The galaxy center and position angle, which gives the orientation of the MGE with respect to the original image, are given in table \ref{tab:galaxyparameters}. This MGE is used in the dynamical modelling in \S ???.  The first column gives the total F814W luminosity of the Gaussian in Eq. (\ref{eq:centralItotalL}) in units of counts. The second column is the corresponding I-band peak surface brightness in Eq. (\ref{eq:MGEgeneral}) in units of a luminosity surface density, calculated from the first column following the procedure described in \S ???. The third and fourth column give the dispersion and the last column the axis ratio of the Gaussian in Eq. (\ref{eq:MGEgeneral}).}
\begin{tabular}{cccccc}
\hline
 & total luminosity  & surface density & \multicolumn{2}{c}{Gaussian dispersion} & axis ratio\\
$k$  & $L_k$ [counts] & $I_{0,k}$ [$L_\odot$/pc$^2$] & $\sigma_k$ [arcsec] & $\sigma_k$ [kpc] & $q'_k$\\\hline
1  &     9425.96 &      20768.  &  0.051   & 0.103  & 1.00\\
2  &    13173.0 &        3161.2 &  0.178   & 0.358  & 0.76\\
3  &    40235.0 &        1588.2 &  0.503   & 1.008  & 0.58\\
4  &    67755.2 &         502.25&  1.180   & 2.368  & 0.56\\
5  &    203677. &         136.51&  3.891   & 7.805  & 0.57\\\hline
\end{tabular}
\label{tab:MGEF814W}
\end{table*}

@@

In \S ??? we derived a mass model for J1331 from Lensing. In this section set up a model for the galaxy's intrinsic light distribution in terms of an MGE, which we will then compare to the mass distribution. The light model will also be the basis of the dynamical Jeans modelling in \S ???.
\\To derive J1331's surface brightness distribution, we use the HST image in the infrared F814W filter, shown in Fig. \ref{fig:F814W}. In infrared J1331's central old and smooth stellar component is more extended than in the F450W filter in Fig. \ref{fig:F450W}, which is more sensitive to young clumpy star-forming regions. In infrared the bulge is also much brighter than the bluish lens images and the imaging is less prone to extinction. The F814W image is therefore best suited for fitting a MGE.

\paragraph{PSF for the HST/F814W filter.} We find a radial profile for the HST/F814W filter PSF from circular annuli within a synthetic PSF image from [TO DO: Where did we get this image from???], ignoring diffraction spikes. The one-dimensional MGE fit of Eq. (\ref{eq:PSFgeneral}) to this radial profile is performed using the code by [TO DO: REF and footnote to code]. The MGE parameters of the normalized PSF model are given in Tab. \ref{tab:PSFMGEF814W}.

\paragraph{MGE for the inner regions.} We fit a MGE to the smooth central region within radius $\sim 5$ arcsec of the HST/WFPC2/WF3/F814W image of J1331 in Fig. \ref{fig:F814W}. Bright objects  close to the galaxy, blobs possibly belonging to the background galaxy and parts of the foreground spiral arm were masked during the fit. J1331's galaxy center, position angle and average apparent ellipticity (see table \ref{tab:galaxyparameters}) are found from the images weighted first and second moment. The MGE fit, as performed by the code \cite{Cap02}, splits the image in annuli with the given ellipticity and position angle and sectors of $5^\circ$ width and fits an 5-Gaussian MGE of the form in Eq. (\ref{eq:MGEgeneral}) convolved with the PSF MGE in table \ref{tab:PSFMGEF814W} to it. The best fit MGE (PSF convolved) is compared to the data in Fig. \ref{fig:MGEinnerRegions} and the corresponding parameters of the intrinsic surface brightness distribution are given in table \ref{tab:MGEF814W}. The fit is a very good representation of the light distribution in the inner 5 arcsec, but underestimates the light distribution outside of this.

@@

\paragraph{Total luminosity and effective radius.} J1331's total I-band luminosity is easily determined by summing up the luminosity contributions of all the Gaussians of the MGE for the outer regions (shown as gray lines in Fig. \ref{fig:MGEouterRegions}). We find $L_\text{tot,I} \simeq 5.6 \cdot 10^{10} L_\odot$. This corresponds to an apparent magnitude of $m_I = 15.77$ mag. We determine the circularized effective radius $R_\text{eff}$ of J1331 from the definition $L(<R_\text{eff}) \equiv \frac 12 L_\text{tot}$ and the growth curve $L(<R)$ from the MGE model of the outer regions [TO DO: Maybe I need a table anyway???], where $R$ is the projected radius on the sky [TO DO: Or is it $R'$???]. We find the effective radius to be $R_\text{eff} \simeq 2.6 \text{arcsec} \hat{=} 5.2 \text{kpc}$.  All values are summarized in Table \ref{tab:galaxyparameters}.

>>>>

\subsection{Surface Photometry for J1331 with MGEs} \label{sec:MGE_results}

@@

\begin{figure}
\centering
\includegraphics[width=0.8\columnwidth]{fig/1331F814Wsci_MGE_M.ps}
\caption{MGE for J1331's inner regions: Comparison of contours with constant F814W surface brightness of J1331's central region (orange lines) with the corresponding iso-brightness contours of the best fit MGE in Table \ref{tab:MGEF814W}, convolved with the PSF in Table \ref{tab:MGEF814W}, (gray lines). The MGE model is a good representation of the galaxy's light distribution within $\sim 5$ arcsec. Image scaling and orientation are indicated in the figure. The black line has a length of 10 arcsec and it's orientation corresponds to the galaxy's position angle as found in Table \ref{tab:galaxyparameters}. For comparison the Einstein radius as found in Table \ref{tab:bestfitlensmodel}  is indicated as red dashed line. This MGE is used in the dynamical Jeans modelling in Sections \ref{sec:results_JAM_SB} and \ref{sec:results_JAM_NFW}. [TO DO: explain how this MGE is used in dynamical modelling]}
\label{fig:MGEinnerRegions}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=0.8\columnwidth]{fig/1331F814W_MGE_disk_L.ps}
\caption{MGE for J1331's outer regions: Comparison of contours with constant surface brightness of the smooth IRAF ELLIPSE model for J1331 in the F814W filter (yellow) with a corresponding best fit MGE (gray lines). The green box corresponds to the image section shown in Figure \ref{fig:MGEinnerRegions}, with the Einstein radius as dashed red line. [TO DO: caption]}
\label{fig:MGEouterRegions}
\end{figure}

@@

\begin{table}
\centering
\caption{F814W PSF MGE: Parameters of the circular four-Gaussian MGE in Equation \ref{eq:PSFgeneral} fitted to the radial profile of the synthetic HST/F814W PSF image by [TO DO].}
\begin{tabular}{ccc}
\hline
$k$ & $G_k$ & $\delta_k$ [arcsec] \\\hline
1 & 0.184 & 0.038\\
2 & 0.485 & 0.085\\
3 & 0.222 & 0.169\\
4 & 0.109 & 0.487\\\hline
\end{tabular}
\label{tab:PSFMGEF814W}
\end{table}

\begin{table*}
\centering
\caption{J1331's F814W MGE: Parameters of the best fit MGE to the F814W surface brightness of J1331 in Figure \ref{fig:F814W}. The fit is best inside an radius of 5 arcsec. The galaxy center and position angle, which gives the orientation of the MGE with respect to the original image, are given in Table \ref{tab:galaxyparameters}. This MGE is used in the dynamical modelling in Sections \ref{sec:results_JAM_SB} and \ref{sec:results_JAM_NFW}.  The first column gives the total F814W luminosity of the Gaussian in Equation \ref{eq:centralItotalL} in units of counts. The second column is the corresponding I-band peak surface brightness in Equation \ref{eq:MGEgeneral} in units of a luminosity surface density, calculated from the first column following the procedure described in Section \ref{sec:MGE_results}. The third and fourth column give the dispersion and the last column the axis ratio of the Gaussian in Equation \ref{eq:MGEgeneral}.}
\begin{tabular}{cccccc}
\hline
 & total luminosity  & surface density & \multicolumn{2}{c}{Gaussian dispersion} & axis ratio\\
$k$  & $L_k$ [counts] & $I_{0,k}$ [$L_\odot$/pc$^2$] & $\sigma_k$ [arcsec] & $\sigma_k$ [kpc] & $q'_k$\\\hline
1  &     9425.96 &      20768.  &  0.051   & 0.103  & 1.00\\
2  &    13173.0 &        3161.2 &  0.178   & 0.358  & 0.76\\
3  &    40235.0 &        1588.2 &  0.503   & 1.008  & 0.58\\
4  &    67755.2 &         502.25&  1.180   & 2.368  & 0.56\\
5  &    203677. &         136.51&  3.891   & 7.805  & 0.57\\\hline
\end{tabular}
\label{tab:MGEF814W}
\end{table*}

@@

In Section \ref{sec:results_lensing} we will derive a mass model for J1331 from Lensing. In this section set up a model for the galaxy's intrinsic light distribution in terms of an MGE, which we will then compare in Section \ref{sec:results_lensing} to the mass distribution. The light model will also be the basis of the dynamical Jeans modelling in Sections \ref{sec:results_JAM_SB} and \ref{sec:results_JAM_NFW}.
\\To derive J1331's surface brightness distribution, we use the HST image in the infrared F814W filter, shown in Figure \ref{fig:F814W}. In infrared J1331's central old and smooth stellar component is more extended than in the F450W filter in Figure \ref{fig:F450W}, which is more sensitive to young clumpy star-forming regions. In infrared the bulge is also much brighter than the bluish lens images and the imaging is less prone to extinction. The F814W image is therefore best suited for fitting a MGE.

\paragraph{PSF for the HST/F814W filter.} We find a radial profile for the HST/F814W filter PSF from circular annuli within a synthetic PSF image from [TO DO: Where did we get this image from???], ignoring diffraction spikes. The one-dimensional MGE fit of Equation \ref{eq:PSFgeneral} to this radial profile is performed using the code by [TO DO: REF and footnote to code]. The MGE parameters of the normalized PSF model are given in Table \ref{tab:PSFMGEF814W}.

\paragraph{MGE for the inner regions.} We fit a MGE to the smooth central region within radius $\sim 5$ arcsec of the HST/WFPC2/WF3/F814W image of J1331 in Figure \ref{fig:F814W}. Bright objects  close to the galaxy, blobs possibly belonging to the background galaxy and parts of the foreground spiral arm were masked during the fit. J1331's galaxy center, position angle and average apparent ellipticity (see Table \ref{tab:galaxyparameters}) are found from the images weighted first and second moment. The MGE fit, as performed by the code \cite{Cap02}, splits the image in annuli with the given ellipticity and position angle and sectors of $5^\circ$ width and fits an 5-Gaussian MGE of the form in Equation \ref{eq:MGEgeneral} convolved with the PSF MGE in Table \ref{tab:PSFMGEF814W} to it. The best fit MGE (PSF convolved) is compared to the data in Figure \ref{fig:MGEinnerRegions} and the corresponding parameters of the intrinsic surface brightness distribution are given in Table \ref{tab:MGEF814W}. The fit is a very good representation of the light distribution in the inner 5 arcsec, but underestimates the light distribution outside of this.

@@

\paragraph{Total luminosity and effective radius.} J1331's total I-band luminosity is easily determined by summing up the luminosity contributions of all the Gaussians of the MGE for the outer regions (shown as gray lines in Figure \ref{fig:MGEouterRegions}). We find $L_\text{tot,I} \simeq 5.6 \cdot 10^{10} L_\odot$. This corresponds to an apparent magnitude of $m_I = 15.77$ mag. We determine the circularized effective radius $R_\text{eff}$ of J1331 from the definition $L(<R_\text{eff}) \equiv \frac 12 L_\text{tot}$ and the growth curve $L(<R')$ from the MGE model of the outer regions [TO DO: Maybe I need a table anyway???], where $R'$ is the projected radius on the sky. We find the effective radius to be $R_\text{eff} \simeq 2.6 \text{ arcsec } \hat{=} 5.2 \text{ kpc}$.  All values are summarized in Table \ref{tab:galaxyparameters}.
